sentiment-analysis

### 2016-08-09 eda/sentiment-analysis.Rmd
loess vs line

This is pretty informative, but I want to see these words plotted by their valence score and average Yelp rating to visualize if there's a positive correlation here between sentiment score and their star rating. 
```{r fig.height = 7}
# boxplot again?
# see specific words and overall trend
# line doesn't fit that well but shows positive trend so best fit
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "loess", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6)
```

>>>>

This is pretty informative, but I want to see these words plotted by their valence score and average Yelp rating to visualize if there's a positive correlation here between sentiment score and their star rating. 
```{r fig.height = 7}
# boxplot again?
# see specific words and overall trend
# line best fit - shows general trend
# loess not good fit
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6)
```
